Model LF

### 2022-11-03 max_dp endogen stød.Rmd
Commit

#### Sensitivity analysis variables 
sens1_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens1_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens3_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
disc=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

COMMENT> Sensitivitets analyse
IDENTITY> sens3_low
EQ> sens3_low = sens3_low*1

@@

COMMENT> 
BEHAVIORAL> emp
EQ> emp = p_250 * (yk/prodk) 
COEFF> p_250 
STORE> coe(14)

@@

COMMENT> 
BEHAVIORAL> prod_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_shock) = + pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_shock,2))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_8 pr_9 pr_10 pr_11
STORE> coe(222)

COMMENT> 
BEHAVIORAL> prod_shock_sens
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_shock_sens) = prs_0 + prs_1* TSDELTALOG(TSLAG(prod_shock,2)) + prs_2* TSDELTALOG(TSLAG(prod_shock,3))  + prs_8* LOG(TSLAG(dp_person,1)) + prs_9* TSLAG(s_h,1) + prs_10* LOG(TSLAG(prod_shock,1)) + prs_11 * d_2007q4
RESTRICT> prs_8 = 0.1
COEFF> prs_0 prs_1 prs_2 prs_8 prs_9 prs_10 prs_11
STORE> coe(24)

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
if> shock_prod_model <= 0
IDENTITY> prod
EQ> prod= prod_shock
if> shock_prod_model > 0
IDENTITY> prod
EQ> prod= prod_shock_sens
if> shock_prod_model > 0 & sens3_low > 0

@@

COMMENT> 
IDENTITY> prod_ds
EQ> prod_ds = prodk_ds * (y_ds/yk_ds)
IF> shock_prod_model <= 0
IDENTITY> prod_ds
EQ> prod_ds =  prod - (alpha_150 + alpha_151*SD1 + alpha_152*SD2 + alpha_153*SD3) + mean_prod
IF> shock_prod_model > 0

@@

  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens3_low = TIMESERIES(c(sens3_low),   
                       START=c(2005,2),FREQ=4),
  disc = TIMESERIES(c(disc),   
                       START=c(2005,2),FREQ=4),
  ## max_dp

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4)
)
```

@@

#S_modelData$prod_shock = prod_ds

@@

yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod

@@

plot(yk_ds_bs3, col= "green"); lines(yk_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

```{r}
###Gengivelse af stød til model
max_dp_sb_low = sens_1_base_low$simulation$max_dp
wage_sb_low = sens_1_base_low$simulation$wage
komp_r_sb_low = sens_1_base_low$simulation$komp_r
part_sb_low = sens_1_base_low$simulation$part
yk_ds_sb_low = sens_1_base_low$simulation$yk_ds
pc_ds_sb_low = sens_1_base_low$simulation$pc_ds
emp_sb_low = sens_1_base_low$simulation$emp
dp_person_sb_low = sens_1_base_low$simulation$dp_person
nl_g_sb_low = sens_1_base_low$simulation$nl_g
```

```{r}
plot(yk_ds_sb_low, col= "red");
lines(yk_ds_00, col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()

```{r}
plot(dp_person_sb_low, col= "red", ylim= c(35,60));
lines(dp_person_00, col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s1_low = sens_1_S1_low$simulation$max_dp
wage_s1_low = sens_1_S1_low$simulation$wage
komp_r_s1_low = sens_1_S1_low$simulation$komp_r
part_s1_low = sens_1_S1_low$simulation$part
yk_ds_s1_low = sens_1_S1_low$simulation$yk_ds
pc_ds_s1_low = sens_1_S1_low$simulation$pc_ds
emp_s1_low = sens_1_S1_low$simulation$emp
dp_person_s1_low = sens_1_S1_low$simulation$dp_person
nl_g_s1_low = sens_1_S1_low$simulation$nl_g
```

```{r}
plot((komp_r_s1_low/komp_r_sb_low), col= "red", main= "Compensation rate");
lines((komp_r_01/komp_r_00), col="black");
legend("top", legend=c("Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((yk_ds_s1_low/yk_ds_sb_low), col= "red", ylim= c(1,1.00010), xlab= "Year", ylab= "Change in GDP", main= "GDP");
lines((yk_ds_01/yk_ds_00), col="black");
legend("top", legend=c("Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((dp_person_s1_low/dp_person_sb_low), col= "red", xlab= "Year", ylab= "Change in GDP", main= "GDP");
lines((dp_person_01/dp_person_00), col="black");
legend("top", legend=c("Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((emp_s1_low-emp_sb_low)*1000, col= "red")
```

```{r}
plot((nl_g_s1_low-nl_g_sb_low), col= "red")
```

@@

```{r}
###Gengivelse af stød til model
max_dp_sb_up = sens_1_base_up$simulation$max_dp
wage_sb_up = sens_1_base_up$simulation$wage
komp_r_sb_up = sens_1_base_up$simulation$komp_r
part_sb_up = sens_1_base_up$simulation$part
yk_ds_sb_up = sens_1_base_up$simulation$yk_ds
pc_ds_sb_up = sens_1_base_up$simulation$pc_ds
emp_sb_up = sens_1_base_up$simulation$emp
dp_person_sb_up = sens_1_base_up$simulation$dp_person
nl_g_sb_up = sens_1_base_up$simulation$nl_g
```

```{r}
plot(yk_ds_sb_up, col= "red");
lines(yk_ds_00, col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()

```{r}
plot(dp_person_sb_up, col= "red", ylim= c(35,60));
lines(dp_person_00, col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s1_up = sens_1_S1_up$simulation$max_dp
wage_s1_up = sens_1_S1_up$simulation$wage
komp_r_s1_up = sens_1_S1_up$simulation$komp_r
part_s1_up = sens_1_S1_up$simulation$part
yk_ds_s1_up = sens_1_S1_up$simulation$yk_ds
pc_ds_s1_up = sens_1_S1_up$simulation$pc_ds
emp_s1_up = sens_1_S1_up$simulation$emp
dp_person_s1_up = sens_1_S1_up$simulation$dp_person
nl_g_s1_up = sens_1_S1_up$simulation$nl_g
```

```{r}
plot((komp_r_s1_up/komp_r_sb_up), col= "red", main= "Compensation rate");
lines((komp_r_01/komp_r_00), col="black");
legend("top", legend=c("Estimate 0.99",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((yk_ds_s1_up/yk_ds_sb_up), col= "red", ylim= c(1,1.00010), xlab= "Year", ylab= "Change in GDP", main= "GDP");
lines((yk_ds_01/yk_ds_00), col="black");
legend("top", legend=c("Estimate 0.99",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((dp_person_s1_up/dp_person_sb_up), col= "red", xlab= "Year", ylab= "Change in GDP", main= "GDP");
lines((dp_person_01/dp_person_00), col="black");
legend("top", legend=c("Estimate 0.99",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((emp_s1_up-emp_sb_up)*1000, col= "red")
```

```{r}
plot((nl_g_s1_up-nl_g_sb_up), col= "red")
```

@@

We change the wage gap allowed to be 38%.

@@

```{r}
###Gengivelse af stød til model
max_dp_sbs2_low = sens_2_bs_low$simulation$max_dp
wage_sbs2_low = sens_2_bs_low$simulation$wage
komp_r_sbs2_low = sens_2_bs_low$simulation$komp_r
part_sbs2_low = sens_2_bs_low$simulation$part
yk_ds_sbs2_low = sens_2_bs_low$simulation$yk_ds
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
wage_ds_t_sbs2_low = sens_2_bs_low$simulation$wage_ds_t
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
max_gap_sbs2_low = sens_2_bs_low$simulation$max_gap
wage_gap1_sbs2_low = sens_2_bs_low$simulation$wage_gap1
inflation_sbs2_low = sens_2_bs_low$simulation$inflation
wage_ds_sbs2_low = sens_2_bs_low$simulation$wage_ds
emp_sbs2_low = sens_2_bs_low$simulation$emp
nl_g_sbs2_low = sens_2_bs_low$simulation$nl_g

unemp_sbs2_low = sens_2_bs_low$simulation$unemp
ik_sbs2_low = sens_2_bs_low$simulation$ik
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s2_low = sens_2_S1_low$simulation$max_dp
wage_s2_low = sens_2_S1_low$simulation$wage
komp_r_s2_low = sens_2_S1_low$simulation$komp_r
emp_s2_low = sens_2_S1_low$simulation$emp
yk_ds_s2_low = sens_2_S1_low$simulation$yk_ds
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
wage_ds_t_s2_low = sens_2_S1_low$simulation$wage_ds_t
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
max_gap_s2_low = sens_2_S1_low$simulation$max_gap
wage_ds_s2_low = sens_2_S1_low$simulation$wage_ds
wage_gap1_s2_low = sens_2_S1_low$simulation$wage_gap1
wage_gap_s2_low = sens_2_S1_low$simulation$wage_gap
nl_g_s2_low = sens_2_S1_low$simulation$nl_g
inflation_s2_low = sens_2_S1_low$simulation$inflation
unemp_s2_low = sens_2_S1_low$simulation$unemp
ik_s2_low = sens_2_S1_low$simulation$ik
```

@@

```{r}
plot(wage_gap1_s2_low, col= "red", main= "Wage-gap (40%) inclusive inflation", ylab= "Wage-gap in % of wage" );grid()
```

```{r}
plot((unemp_s2_low-unemp_sbs2_low)*1000, col= "red")
```
Effekten er faktisk større når gab er lavere da løn niveauet så er lavere når stødet stiger og derved har stødet en større effekt!!!

Effect on government net lending:

```{r}
plot((nl_g_s2_low-nl_g_sbs2_low), col= "red")
```

@@

```{r}
plot((wage_ds_t_s2_up/wage_ds_t_sbs2_up), col= "red", ylim= c(1, 1.05), main= "Targeted Wage");
lines((wage_ds_t_02/wage_ds_t_bs2), col="black");
legend("top", legend=c("Wage-gap limit 44%",
                       "Wage-gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((inflation_s2_up-inflation_sbs2_up), col= "red", ylim= c(-0.0004, 0.0035), main= "Inflation");
lines((inflation_02-inflation_bs2), col="black");
legend("top", legend=c("Wage-gap limit 42%",
                       "Wage-gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((wage_ds_s2_up/wage_ds_sbs2_up), col= "red", ylim= c(0.995, 1.04), main= "Wage");
lines((wage_ds_02/wage_ds_bs2), col="black");
legend("top", legend=c("Wage-gap limit 42%",
                       "Wage-gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((u_ds_s2_up/u_ds_sbs2_up), col= "red", ylim= c(0.998, 1.005), main= "Capacity utilization");
lines((u_ds_02/u_ds_bs2), col="black");
legend("top", legend=c("Wage-gap limit 42%",
                       "Wage-gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((ik_s2_up/ik_sbs2_up), col= "red", main= "% Change in Investments");
lines((ik_02/ik_bs2), col="black");
legend("left", legend=c("Wage Gap limit 42%",
                       "Wage gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((pconk_ds_s2_up/pconk_ds_sbs2_up), col= "red", main= "% change in Consumption");
lines((pconk_ds_02/pconk_ds_bs2), col="black");
legend("left", legend=c("Wage Gap limit 42%",
                       "Wage gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((net_balance_s2_up/net_balance_sbs2_up), col= "red", main= "% Change in net Trade balance");
lines((net_balance_02/net_balance_bs2), col="black");
legend("left", legend=c("Wage Gap limit 42%",
                       "Wage gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

```{r}
plot((emp_s2_up-emp_sbs2_up)*1000, col= "red", main= "Change in employed (people)");grid()
```

```{r}
plot((nl_g_s2_up-nl_g_sbs2_up), col= "red")
```

@@

We change the estimate in prod function to 0.1.

>>>>

#### Sensitivity analysis variables 
sens1_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens1_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens_3=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
disc=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

COMMENT> Sensitivitets analyse
IDENTITY> sens_3
EQ> sens_3 = sens_3*1

@@

COMMENT> 
BEHAVIORAL> emp_old
EQ> emp_old = p_250 * (yk/prodk) 
COEFF> p_250 
STORE> coe(14)

COMMENT> 
BEHAVIORAL> emp_sens
EQ> emp_sens = p_251 * (yk/prodk) 
COEFF> p_251 
RESTRICT> p_251 = 0.5
STORE> coe(144)

COMMENT> 
IDENTITY> emp
EQ> emp = emp_old
IF> sens_3 <= 0
IDENTITY> emp
EQ> emp = emp_sens
IF> sens_3 > 0

@@

COMMENT> 
BEHAVIORAL> prod_ds_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_shock) = + pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_shock,2))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_8 pr_9 pr_10 pr_11
STORE> coe(222)

COMMENT> 
BEHAVIORAL> prod_ds_sens
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_sens) = + pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_sens,2))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_8 pr_9 pr_10 pr_11
RESTRICT> pr_9 = 0.03
STORE> coe(223)

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
if> shock_prod_model <= 0
IDENTITY> prod
EQ> prod =  prod_ds +alpha_150 + alpha_151*SD1 + alpha_152*SD2 + alpha_153*SD3 - mean_prod
IF> shock_prod_model > 0

@@

COMMENT> 
IDENTITY> prod_ds
EQ> prod_ds = prodk_ds * (y_ds/yk_ds)
IF> shock_prod_model <= 0
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_shock
if> shock_prod_model > 0 & sens_3 <= 0
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_sens
if> shock_prod_model > 0 & sens_3 > 0

@@

  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens_3 = TIMESERIES(c(sens_3),   
                       START=c(2005,2),FREQ=4),
  disc = TIMESERIES(c(disc),   
                       START=c(2005,2),FREQ=4),
  ## max_dp

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_ds_shock = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4)
)
```

@@

#S_modelData$prod_ds_sens = prod_ds

@@

yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
prod_ds_bs3 = Shock_bs3$simulation$prod_ds
prod_ds_shock_bs3 = Shock_bs3$simulation$prod_ds_shock

@@

plot(prod_bs3, col= "green"); lines(prod_ds_shock_bs3, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

```{r}
###Gengivelse af stød til model
max_dp_sb_low = sens_1_base_low$simulation$max_dp
wage_sb_low = sens_1_base_low$simulation$wage
komp_r_sb_low = sens_1_base_low$simulation$komp_r
part_sb_low = sens_1_base_low$simulation$part
yk_ds_sb_low = sens_1_base_low$simulation$yk_ds
pc_ds_sb_low = sens_1_base_low$simulation$pc_ds
unemp_sb_low = sens_1_base_low$simulation$unemp
dp_person_sb_low = sens_1_base_low$simulation$dp_person
nl_g_sb_low = sens_1_base_low$simulation$nl_g
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s1_low = sens_1_S1_low$simulation$max_dp
wage_s1_low = sens_1_S1_low$simulation$wage
komp_r_s1_low = sens_1_S1_low$simulation$komp_r
part_s1_low = sens_1_S1_low$simulation$part
yk_ds_s1_low = sens_1_S1_low$simulation$yk_ds
pc_ds_s1_low = sens_1_S1_low$simulation$pc_ds
unemp_s1_low = sens_1_S1_low$simulation$unemp
dp_person_s1_low = sens_1_S1_low$simulation$dp_person
nl_g_s1_low = sens_1_S1_low$simulation$nl_g
```

@@

```{r}
###Gengivelse af stød til model
max_dp_sb_up = sens_1_base_up$simulation$max_dp
wage_sb_up = sens_1_base_up$simulation$wage
komp_r_sb_up = sens_1_base_up$simulation$komp_r
part_sb_up = sens_1_base_up$simulation$part
yk_ds_sb_up = sens_1_base_up$simulation$yk_ds
pc_ds_sb_up = sens_1_base_up$simulation$pc_ds
unemp_sb_up = sens_1_base_up$simulation$unemp
dp_person_sb_up = sens_1_base_up$simulation$dp_person
nl_g_sb_up = sens_1_base_up$simulation$nl_g
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s1_up = sens_1_S1_up$simulation$max_dp
wage_s1_up = sens_1_S1_up$simulation$wage
komp_r_s1_up = sens_1_S1_up$simulation$komp_r
part_s1_up = sens_1_S1_up$simulation$part
yk_ds_s1_up = sens_1_S1_up$simulation$yk_ds
pc_ds_s1_up = sens_1_S1_up$simulation$pc_ds
unemp_s1_up = sens_1_S1_up$simulation$unemp
dp_person_s1_up = sens_1_S1_up$simulation$dp_person
nl_g_s1_up = sens_1_S1_up$simulation$nl_g
```

## Sens 1 plots

```{r}
plot((yk_ds_s1_up/yk_ds_sb_up), col= "red", ylim= c(1,1.00010), xlab= "Year", ylab= "Change in GDP", main= "Sensitivity of GDP");
lines((yk_ds_s1_low/yk_ds_sb_low), col="black");
lines((yk_ds_01/yk_ds_00), col="blue");
legend("top", legend=c("Estimate 0.99",
                       "Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

Effect on unemployment:

```{r}
plot((unemp_s1_up-unemp_sb_up)*1000, col= "red", xlab= "Year", ylab= "Change in Unemployment (people)", main= "Sensitivity of Unemployment");
lines((unemp_s1_low-unemp_sb_low)*1000, col="black");
lines((unemp_01-unemp_00)*1000, col="blue");
legend("left", legend=c("Estimate 0.99",
                       "Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()

@@

@@

```{r}
###Gengivelse af stød til model
max_dp_sbs2_low = sens_2_bs_low$simulation$max_dp
wage_sbs2_low = sens_2_bs_low$simulation$wage
komp_r_sbs2_low = sens_2_bs_low$simulation$komp_r
part_sbs2_low = sens_2_bs_low$simulation$part
yk_ds_sbs2_low = sens_2_bs_low$simulation$yk_ds
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
wage_ds_t_sbs2_low = sens_2_bs_low$simulation$wage_ds_t
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
max_gap_sbs2_low = sens_2_bs_low$simulation$max_gap
wage_gap1_sbs2_low = sens_2_bs_low$simulation$wage_gap1
inflation_sbs2_low = sens_2_bs_low$simulation$inflation
wage_ds_sbs2_low = sens_2_bs_low$simulation$wage_ds
emp_sbs2_low = sens_2_bs_low$simulation$emp
nl_g_sbs2_low = sens_2_bs_low$simulation$nl_g
pconk_ds_sbs2_low = sens_2_bs_low$simulation$pconk_ds
unemp_sbs2_low = sens_2_bs_low$simulation$unemp
ik_sbs2_low = sens_2_bs_low$simulation$ik
xk_sbs2_low = sens_2_bs_low$simulation$xk
mk_sbs2_low = sens_2_bs_low$simulation$mk

net_export_sbs2_low= xk_sbs2_low - mk_sbs2_low

@@

```{r}
###Gengivelse af stød til model
max_dp_s2_low = sens_2_S1_low$simulation$max_dp
wage_s2_low = sens_2_S1_low$simulation$wage
komp_r_s2_low = sens_2_S1_low$simulation$komp_r
emp_s2_low = sens_2_S1_low$simulation$emp
yk_ds_s2_low = sens_2_S1_low$simulation$yk_ds
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
wage_ds_t_s2_low = sens_2_S1_low$simulation$wage_ds_t
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
max_gap_s2_low = sens_2_S1_low$simulation$max_gap
wage_ds_s2_low = sens_2_S1_low$simulation$wage_ds
wage_gap1_s2_low = sens_2_S1_low$simulation$wage_gap1
wage_gap_s2_low = sens_2_S1_low$simulation$wage_gap
nl_g_s2_low = sens_2_S1_low$simulation$nl_g
inflation_s2_low = sens_2_S1_low$simulation$inflation
unemp_s2_low = sens_2_S1_low$simulation$unemp
ik_s2_low = sens_2_S1_low$simulation$ik
pconk_ds_s2_low = sens_2_S1_low$simulation$pconk_ds

xk_s2_low = sens_2_S1_low$simulation$xk
mk_s2_low = sens_2_S1_low$simulation$mk

net_export_s2_low= xk_s2_low - mk_s2_low
```

@@

Effect on unemployment:

```{r}
plot((unemp_s2_low-unemp_sbs2_low)*1000, col= "red")
```

@@

## Sens 2 plots

```{r}
plot((wage_ds_t_s2_up/wage_ds_t_sbs2_up), col= "red", ylim= c(1, 1.05), main= "Targeted Wage");
lines((wage_ds_t_s2_low/wage_ds_t_sbs2_low), col="black");
lines((wage_ds_t_02/wage_ds_t_bs2), col="blue");
legend("top", legend=c("Wage-gap limit 44%",
                       "Wage-gap limit 40%",
                       "Wage-gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

```{r}
plot((wage_ds_s2_up/wage_ds_sbs2_up), col= "red", ylim= c(0.995, 1.04), main= "Wage");
lines((wage_ds_s2_low/wage_ds_sbs2_low), col="black");
lines((wage_ds_02/wage_ds_bs2), col="blue");
legend("top", legend=c("Wage-gap limit 44%",
                       "Wage-gap limit 40%",
                       "Wage-gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

```{r}
plot((ik_s2_up - ik_sbs2_up), col= "red", main= "% Change in Investments");
lines((ik_s2_low - ik_sbs2_low), col="black");
lines((ik_02 - ik_bs2), col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

```{r}
plot((pconk_ds_s2_up - pconk_ds_sbs2_up), col= "red", main= "% Change in Consumption");
lines((pconk_ds_s2_low - pconk_ds_sbs2_low), col="black");
lines((pconk_ds_02 - pconk_ds_bs2), col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

```{r}
plot((net_balance_s2_up - net_balance_sbs2_up), col= "red", main= "% Change in Net exports");
lines((net_export_s2_low - net_export_sbs2_low), col="black");
lines((net_balance_02 - net_balance_bs2), col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

@@

Effect on unemployment:

```{r}
plot((unemp_s2_up-unemp_sbs2_up)*1000, col= "red", main= "Change in employed (people)");grid()
```

@@

We change the estimate in prod function to 0.3 and the estimate in employment function to 0.5
